---
title: "Basic Descriptive Statistics using R"
author: "siju.swamy@saintgits.org"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
footer: "Copyright (c) 2023, saintgits"
css: custom.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Introduction

- Descriptive statistics (in the broad sense of the term) is a branch of statistics aiming at summarizing, describing and presenting a series of values or a dataset.

- Descriptive statistics is often the first step and an important part in any statistical analysis.

- It allows to check the quality of the data and it helps to “understand” the data by having a clear overview of it.

- If well presented, descriptive statistics is already a good starting point for further analyses.

## Types of Descriptive Summary

There exists many measures to summarize a dataset. They are divided into two types:

- location measures and

- dispersion measures

## Working with Toy Dataset


As a first step load the data set to R:

```{r}
dat <- iris # load the iris dataset and renamed it dat
```

```{r}
head(dat) # first 6 observations
```

## Structure of a dataset

```{r}
str(dat) # structure of dataset

```


## Basic summary statistics

```
min, max, mean, median, range, IQR, quantiles

```

```{r}
print("Minimum")
min(dat$Sepal.Length)
median(dat$Sepal.Length)
quantile(dat$Sepal.Length, c(0.25,0.5,0.75)) # three quartile
```


## Standard deviation and variance

> The standard deviation and the variance is computed with the `sd()` and `var()` functions:

```{r}
sd(dat$Sepal.Length)
var(dat$Sepal.Length)
sqrt(var(dat$Sepal.Length))
```

>**Tip:** to compute the standard deviation (or variance) of multiple variables at the same time, use `lapply()` with the appropriate statistics as second argument:

```{r}
lapply(dat[, 1:4], sd)
```

## Five point Summary

```{r}
summary(dat)
```

>**Group-wise summary**

```{r}
by(dat, dat$Species, summary)

```

## Coefficient of variation

The coefficient of variation can be found by computing manually (remember that the coefficient of variation is the standard deviation divided by the mean):

```{r}
sd(dat$Sepal.Length) / mean(dat$Sepal.Length)
```
## Mode

```{r}
tab <- table(dat$Sepal.Length) # number of occurrences for each unique value
sort(tab, decreasing = TRUE) # sort highest to lowest
```

## Takeaway

- In R programming, basic descriptive statistic functions are simple and exactly same as in statistical defintions.
