---
title: "Compare Two Variances in R"
author: "siju.swamy@saintgits.org"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T)
```

# Statistical test for variance

F-test is used to assess whether the variances of two populations (A and B) are equal.

**Uses**:

Comparing two variances is useful in several cases, including:

- When you want to perform a two samples t-test to check the equality of the variances of the two samples

- When you want to compare the variability of a new measurement method to an old one. Does the new method reduce the variability of the measure?


# Research questions and statistical hypotheses

Typical research questions are:


- whether the variance of group A ($\sigma^2_A$) is equal to the variance of group B ($\sigma^2_b$)?

- whether the variance of group A ($\sigma^2_A$ is less than the variance of group B ($\sigma^2_A$)?

- whether the variance of group A ($\sigma^2_A$) is greather than the variance of group B ($\sigma^2_A$)?

**Hypothesis**:

In statistics, we can define the corresponding null hypothesis ($H_0$) as follow:

- $H_0:\sigma^2_A=\sigma^2_b$

- $H_0:\sigma^2_A \leq\sigma^2_b$

- $H_0:\sigma^2_A\geq\sigma^2_b$


The corresponding alternative hypotheses ($H_1$) are as follow:

-$H_1:\sigma^2_A\neq\sigma^2_b$ (different)

-$H_1:\sigma^2_A>\sigma^2_b$ (greater)

-$H_1:\sigma^2_A<\sigma^2_b$ (less)

# Requirement of F-test

**Note that, the F-test requires the two samples to be normally distributed.**

The R function *var.test()* can be used to compare two variances and its syntax is same as that of t- test.

two methods can be used:

**Method 1**

var.test(values ~ groups, data, 
         alternative = "two.sided/greater/less")
         
**Method 2**

var.test(x, y, alternative = "two.sided/greater/less")

# Example

To illustrate F- test, I choose ToothGrowth data in R. A random sample of 10 individuals are shown bellow:

```{r}
# Store the data in the variable my_data
my_data <- ToothGrowth
library("dplyr")
sample_n(my_data, 10)
```

#Preleminary test to check F-test assumptions

F-test is very sensitive to departure from the normal assumption. You need to check whether the data is normally distributed before using the F-test.

Shapiro-Wilk test can be used to test whether the normal assumption holds. It's also possible to use Q-Q plot (quantile-quantile plot) to graphically evaluate the normality of a variable. Q-Q plot draws the correlation between a given sample and the normal distribution.

```{r}
shapiro.test(my_data$len)
```
Since p- value is greater than 0.05. So the normality is holds good.

 
If there is doubt about normality, the better choice is to use *Levene's test* or *Fligner-Killeen test*, which are less sensitive to departure from normal assumption.

# Calculating F- test

```{r}
# F-test long method
res.ftest <- var.test(len ~ supp, data = my_data, alternative="two.sided")
res.ftest
```

# Interpretation of the result

The p-value of F-test is $p = 0.2331433$ which is greater than the significance level 0.05. In conclusion, there is no significant difference between the two variances.

